% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\let\nofiles\relax
\documentclass[8pt]{res} 

% TODO -- clean up comments
%\usepackage{bibentry}
%\nobibliography*

\usepackage{hyperref}
\usepackage[a4paper,margin=1.00in]{geometry}
\oddsidemargin = -0.4in % remove extra bit from left margin

\setlength{\textheight}{10.0 in} % increase text height to fit on 1-page 

\begin{document} 

  \name{Juan Luis Burgos\\[12pt]}
  \address{\bf \href{mailto:juanlb1988@gmail.com}{juanlb1988@gmail.com} \texttt{||} \href{https://www.linkedin.com/in/juan-burgos-93658b1b/}{LinkedIn}}

  \begin{resume}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{Education}}          
    \textbf{Bachelor of Science, Texas A\&M University}, May 2013   \\       
    \textbf{Majors:} Computer Engineering and Applied Mathematical Science \\
    \textbf{Overall GPA:} 3.63 / 4.00     

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{Technical Skills}}        
    Familiar with Windows, MacOS, and Linux operating systems. \\
    Experience programming in C/C++, Java, Ruby, Python, Lua, Shell, \LaTeX.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{Relevant Experience}}\vspace{-5pt}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
      \bf Staff Software Engineer \>\bf IBM Corporation \>\bf August 2016 - Present\\ \>\bf Durham, NC
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Developing IBM Cloud Monitoring capabilities for Instana observability and application monitoring.
      \item Developing a dockerized micro-service that manages per tenant configurations.
      \item Worked with international team to integrate data-analytics functionality into the IBM Cloud Pak for Multicloud Management performance monitoring product. 
      \item Worked with APMSaaS DevOps and Infrastructure teams to resolve customer issues, perform infrastructure migrations, and apply PSIRT patches, etc.
      \item Supported multiple backend Ruby on Rails endpoints, maintenance of Apache and Haproxy servers, and inter-service integrations for SaaS products.
      \item Implemented Lua-based Haproxy plugins for several backend infrastructures supporting SaaS products.
    \end{itemize}\vspace{-18pt}      % suppress blank line after tabbing
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
      \bf Backend Engineer \>\bf IBM Corporation \>\bf July 2014 - August 2016\\ \>\bf Durham, NC
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Lead Ruby on Rails developer on our backend endpoint that manages the creation, modification, and destruction of SaaS subscriptions and integration with other services.
      \item Implemented Ruby gem that provided per-process performance monitoring for Ruby on Rails applications for the Application Performance Monitoring on SaaS product.
      \item Implemented backend scripts in Ruby, Perl, and Bash that supported E2E SaaS subscription lifecycle flows.
      \item Implemented web interface providing users with monitoring agent, configuration package, and development tool download capability.
      \item Supported infrastructure team in the introduction of new API flows.
      \item Assisted SaaS Operations team during product releases.
    \end{itemize}\vspace{-18pt}      % suppress blank line after tabbing
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
      \bf Software Engineer \>\bf IBM Corporation \>\bf July 2013 - July 2014\\ \>\bf Durham, NC
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Designed and developed a new Ruby on Rails agent for the Application Performance Monitoring on SaaS product.
      \item Daily interaction with global test teams to address bug reports and new feature requests.
      \item Assisted in the development of other monitoring agents (i.e. MongoDB, PHP).
    \end{itemize}\vspace{-18pt}      % suppress blank line after tabbing
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
      \bf Undergraduate Researcher \>\bf Texas A\&M University \>\bf June 2010 - May 2013\\ \>\bf College Station, TX
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Conducted research in the area of Sampling Based Motion Planning (SBMP) under the guidance of Dr. Nancy Amato.
      \item Worked on multiple research papers and completed senior research thesis as part of my B.S. Computer Engineering degree plan.
      \item Attended multiple research seminars and a Computing conference in Washington D.C.
    \end{itemize}\vspace{-18pt}      % suppress blank line after tabbing
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \pagebreak % So we don't cut off the Matlab stuff below
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
      \bf Matlab Tutor \>\bf Texas A\&M University \>\bf January 2009 - May 2011\\ \>\bf College Station, TX
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Directly tutored both individual students and large groups on concepts ranging from Single to Multi-Variate Calculus, Differential Equations, and Linear Algebra using Matlab and MapleSoft programming languages.
    \end{itemize}\vspace{-18pt}      % suppress blank line after tabbing
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tabbing}
      \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
      \bf SEE Math Camp Counselor \>\bf Texas A\&M University \>\bf June 2009, 2010, 2011\\ \>\bf College Station, TX
    \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
      \item Mentored middle school students in their exploration of the world of mathematics through group activities and MapleSoft programming at annual math-oriented summer camp held by the Texas A\&M Department of Mathematics.
    \end{itemize}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{Honors and Memberships}}          
    \vspace{+0.02in}	
    \emph{Undergraduate Research Fellows Honors}, 2013 \\
    \emph{Engineering Scholar Honors}, 2013 \\
    \emph{University Honors}, 2013 \\
    \emph{Cum Laude Honors}, 2013 \\
    \emph{Upsilon Pi Epsilon Membership}, 2013 \\
    \emph{Dean's List}, 2008 - 2013 \\
    \emph{Distinguished Student Award}, 2010 \\
    \emph{Pi Mu Epsilon Membership}, 2009 \\
    \emph{Title of Computer Science Ambassador}, 2008 - 2009 \& 2010 - 2012 \\
    \emph{Student Engineers' Council}, 2008 - 2011 \\
    \vspace{-0.1in}	

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{Publications}}
    Juan Burgos, Jory Denny, Nancy M. Amato, \emph{"Improving Roadmap Quality through Connected Component \\
    Expansion,"} Technical Report, TR13-003, Texas A\&M University, Apr 2013.

    Samuel Rodriguez, Jory Denny, Juan Burgos, Aditya Mahadevan, Kasra Manavi, Luke Murray, Anton \\
    Kodochygov, Takis Zourntos, Nancy M. Amato, \emph{"Toward Realistic Pursuit-Evasion Using a \\
    Roadmap-Based Approach,"} In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pp. 1738-1745, May 2011. 

    Sam Ade Jacobs, Kasra Manavi, Juan Burgos, Jory Denny, Shawna Thomas, Nancy M. Amato, \emph{"A Scalable \\
    Method for Parallelizing Sampling-Based Motion Planning Algorithms,"} In Proc. IEEE Int. Conf. \\
    Robot. Autom. (ICRA), pp. 2529-2536, St. Paul, Minnesota, USA, May 2012. 

    Samuel Rodriguez, Jory Denny, Aditya Mahadevan, Jeremy (Cong-Trung) Vu, Juan Burgos, \\
    Takis Zourntos, Nancy M. Amato, \emph{"Roadmap-Based Pursuit-Evasion in 3D Structures,"} \\
    In Proc. of 24th Intern. Conf. on Computer Animation and Social Agents (CASA), 2011, \\
    in Transactions on Edutainment, pp. to appear, May 2011.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\underline{References Available Upon Request}}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \end{resume}
\end{document}

